Theories of deliberated choice

### 2023-10-10 simple.tex
More about falsification.

While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
Throughout the article, $\N$ includes zero. %and $\N^* = \N \setminus \set{0}$. 
Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$. A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.

@@

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).

Given a pair $(I, \allargs)$, a general observation $θ$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.

\begin{definition}
  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
  %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
\end{definition}
\begin{example}
  $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:unfals}
  $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:unfals} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

  Consider … (seems redundant).
\end{example}
\begin{remark}
  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable. But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim. I should think about this.
\end{remark}
\begin{remark}
  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
\end{remark}
\begin{theorem}
  A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$, or equivalently:
  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$.
\end{theorem}

Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
Let $M$ denote a maximal $E$.
Any $M$ maps each individual $i \in I$ to an increasing sequence.
Given ${\allleadsto}$, let $E_{\allleadsto} \subseteq {\allleadsto}$ denote the observable compatible sets (triples, not pairs, thus including values). These are the $E$ to which the value associated is the one given by $\allleadsto$.
Define similarly $M_{\allleadsto}$.
Let $X_C \subseteq I × \allhist × P$ denote a subset that is completable to some ${\allleadsto}$ in $C$. It is downwards closed.
Let $N_C$ denote a maximal such subset.
A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $E_{\allleadsto}$ equals some $X_C$.
A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$.
A claim is not falsifiable iff it is possible to pick some $M_{\allleadsto_1}$ from $C$ (that is, a mapping of each individual to an increasing sequence, together with the associated value from $\allleadsto_1$), some other $M_{\allleadsto_2}$ from $C$, and on their common entries (if any) these two relations agree (so their union is a right-unique relation), and so on for each possible mappings $M$, so as to form a complete $\allleadsto$ that is not in $C$.
A claim is falsifiable iff it is closed under the above picking operation.
Equivalently, a claim is not falsifiable iff this can be done for a given number of $M$ whose union is not an $X_C$.
We could need more than two such $M$'s, I suppose: for the theorem below, the number of such $M$'s is equal to the cardinal of the set on which they differ.
TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.

>>>>

While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$. 
Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
Define $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
A generic element of $\allhist$ (a sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
Thus, given an argumentative path $\hist \in \allhist$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$. A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.

@@

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
Let $C^\subseteq = \set{c \subseteq (I × \allhist) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhist)$).
Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.

Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.

Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat \card{A_i} = i \land i < j \implies A_i \subsetneq A_j} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$, thus, a possibly empty embedded sequence of elements in $\allhist$.
Therefore, we let $\incr(\allhist)^I = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}.
Note that $\incr(\allhist)^I$ is downwards closed, meaning that $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.
Let a \emph{simple a priori observation} be defined as an element $O \in (\allhist)^I$.
Given a simple a priori observation $O: I \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in I × \allhist \suchthat \forall i \in I: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$. 
Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.

Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhist)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhist)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
Note that $(\cup_{A \in \max \incr(\allhist)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.

Given a claim $C$, we can also define the set $\Theta \cap C^\subseteq$ of possibilities for increasing sequences corresponding to the claim.
This set is downwards-closed, as both $\Theta$ and $C^\subseteq$ are.

  \begin{definition}
    We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
    %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
    $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
  \end{definition}
  Equivalently, iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$.
  Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
  \begin{example}
    $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
    Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
  \end{example}
  \begin{example}
    \label{ex:unfals}
    $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
    Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
    Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
    By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
  \end{example}
  \begin{example}
    $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
    Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
    \Cref{ex:unfals} concludes.
  \end{example}
  \begin{example}
    Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
    Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
  \end{example}
  \begin{example}
    Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
    Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
  \end{example}
  \begin{example}
    Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
    The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

    Consider … (seems redundant).
  \end{example}
  \begin{remark}
    The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable. But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim. I should think about this.
  \end{remark}
  \begin{remark}
    To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
  \end{remark}
  \begin{theorem}
    A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
    $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
    $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhist)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
  \end{theorem}
\begin{proof}
  The first phrasing follows from the definition of falsifiability.
  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.

  Let us prove that the first phrasing implies the second one.
  Given $\theta$, define $O = \set{(i, \argmax_{\hist \in (\theta(i) \cup \emptyset)} \card{\hist})}$ as associating to each $i$ the longest corresponding $\hist$ from $\theta$, or the empty sequence if $\theta(i)$ is empty.
  It follows that $\theta \subseteq \restr{\allleadstog}{O_O}$.
  Thus, $S_{\restr{\allleadstog}{O_O}} \subseteq S_\theta$.
  As $S_\theta \subseteq \Cbar$, we obtain $S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
\end{proof}
\begin{conjecture}
  Test each $O$ of a given length. If find ${\allleadstog} \in \Cbar \suchthat S_{\restr{\allleadstog}{O_O}} \cap C \neq \emptyset$, and also the more lengthy $O'$ completing $O$ satisfy this, then $C$ is not falsifiable; otherwise, it is.
  Equivalently, pick $k \in \N$, test each $O$ of that length; and proceed for each $k$. Nah.
\end{conjecture}

  \begin{remark}
    Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
    Let $M$ denote a maximal $E$.
    Any $M$ maps each individual $i \in I$ to an increasing sequence.
    Given ${\allleadsto}$, let $E_{\allleadsto} \subseteq {\allleadsto}$ denote the observable compatible sets (triples, not pairs, thus including values). These are the $E$ to which the value associated is the one given by $\allleadsto$.
    Define similarly $M_{\allleadsto}$.
    Let $X_C \subseteq I × \allhist × P$ denote a subset that is completable to some ${\allleadsto}$ in $C$. It is downwards closed.
    Let $N_C$ denote a maximal such subset.
    A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $E_{\allleadsto}$ equals some $X_C$.
    A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$.
    A claim is not falsifiable iff it is possible to pick some $M_{\allleadsto_1}$ from $C$ (that is, a mapping of each individual to an increasing sequence, together with the associated value from $\allleadsto_1$), some other $M_{\allleadsto_2}$ from $C$, and on their common entries (if any) these two relations agree (so their union is a right-unique relation), and so on for each possible mappings $M$, so as to form a complete $\allleadsto$ that is not in $C$.
    A claim is falsifiable iff it is closed under the above picking operation.
    Equivalently, a claim is not falsifiable iff this can be done for a given number of $M$ whose union is not an $X_C$.
    We could need more than two such $M$'s, I suppose: for the theorem below, the number of such $M$'s is equal to the cardinal of the set on which they differ.
    TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.
  \end{remark}
  \begin{remark}
    If $C$ is such that $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$, then $C$ is not falsifiable.
    This looks correct:
    our counter-example has the relation with some $M$ not equal to any $X_C$.

    To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
  \end{remark}
  \begin{conjecture}
    Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
    $C$ is falsifiable iff these new elements are necessarily in $C$.
  \end{conjecture}
  \begin{proof}
    This seems false. (Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
    % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$). Assume that $\cup S$ is total and right-unique and is not in $C$.
    % Let us show that $C$ is not falsifiable.
    % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
    % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
    % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
    % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
  \end{proof}
  \begin{conjecture}
    Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{s^{-1}(P) \suchthat s \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
    $C$ is falsifiable iff all such sets $S$ are in $C$.
  \end{conjecture}
  \begin{proof}
    Consider such $S$.
    Assume that $\cup S$ is right-unique and is not in $C$.
    Let us show that $C$ is not falsifiable.
    Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
    Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$. Thus, $O \in \set{s^{-1}(P) \suchthat s \in S}$. Pick an $s \in S \suchthat s^{-1}(P) = O$. We have $s \in C^\subseteq$ and $\theta^{-1}(P) \subseteq s^{-1}(P)$.
    Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $s$ on its domain. It follows that $\theta \subseteq s$. As $C^\subseteq$ is downwards-closed, this concludes.

    Now, Assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$. Let us exhibit a set $S$ such that $\cup S = {\allleadstog}$.
    Pick any $O \in (\incr(\allhist))^I$ and complete it with values from $\allleadstog$ to obtain a $c$. Now, we know that $C^\subseteq$ contains all finite subsequences of $c$, but it does not follow that it contains the infinite sequence $O$, does it?
    If $C ≠ \emptyset$, an element $c'$ has the same domain as $c$. We know that $c_1 \subseteq c_2 \subseteq …$, where each is a finite subset, is extensible to some function in $C$… ???
  \end{proof}
